### 2021-03-18 Chapter-1/Chapter-1.tex
Updates from Overleaf

\section{Address-based Side-channel}
\subsection{Attack}
Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses. Most of the attack allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim. As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.

@@

\section{Contribution}
We address the above problems from two aspects. First, we propose a novel method that can detect side-channel vulnerabilities in real-world applications automatically fast and precisely. Second, we propose methods that can quantify each side-channel leakages precisely. In additional, we study two kinds of threat models, a single trace attack, and chosen message attacks

>>>>

\section{Address-based Side-channel}
\subsection{Attack}
Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses. Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim. As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.

@@

\section{Contribution}
We address above problems from two aspects. First, we propose a novel method that can detect side-channel vulnerabilities in real-world applications automatically fast and precisely. Second, we propose methods that can quantify each side-channel leakages precisely. In addition, we study two kinds of threat models, single-trace attacks, and chosen message attacks.
